**Density Dependence**

### 2023-03-07 Rmd/report mac.Rmd
checked
updates

Each of the OMs were then projected for the values of $F_{MSY}$ based on the four assumptions about density dependence. This allows a comparison between the yield that could potentially be achieved and that forgone by making an incorrect assumption about density dependence. The OMs were first projected, without process error in recruitment, from the end of the historical estimates for a range of fishing mortality (spanning 0 to $F_{crash}$) for 30 years into the future. The estimates in the final year of the projections were then be used to construct equilibrium curves (**Figure X2**). The points on the curve correspond to the projected outcomes for the values of $F_{MSY}$ from each OM. This was run as a check, as the equilibrium and projections should agree, I.e. the points at MSY should be the same colour as the curve.

The OMs were also projected for the estimates of different estimates $F_{MSY}$, with stochasticty in the recruitment deviates. This allows the impact of misspecification of density dependence to be evaluated, i.e. if $F_{MSY}$ is underestimated then yield will be less than MSY, while if $F_{MSY}$ is overestimated yield will be lost due to overfishing. Stochastic projections of the four Operating Models for the four estimates of $F_{MSY}$ are shown in **Figures X3a, X3b, X3c and X3d**

**Figure X4** summarizes the yields and SSBs obtained for each Operating Model under the correct and mis-specified form of density dependence.

@@

REMOVE 
[ -   The impact of ignoring density dependence ]
[ -   The impact of assuming density-dependence incorrectly ]
[ -   Robustness of the current ICES framework ]

@@

[ CHECK THE FORMULA ] W^'=¯W^-0.18 $W_a = {\overline{W_a}} B^{{\beta}_a}$

@@

$W_a = {\overline{W_a}} B^{{\beta}_a}$

@@

[ NEED TO CHECK THIS FIGURE; IS THIS A PLAUSIBLE RESULT? ]

@@

@@

The OMs were first projected, without process error in recruitment, from the end of the historical estimates for a range of fishing mortality (spanning 0 to $F_{crash}$) for 30 years into the future. The estimates in the final year of the projections were then be used to construct equilibrium curves (**Figure X2**). The points on the curve correspond to the projected outcomes for the values of $F_{MSY}$ from each OM. This was run as a check, as the equilibrium and projections should agree, I.e. the points at MSY should be the same colour as the curve.

The OMs were also projected for the estimates of different estimates $F_{MSY}$, with stochasticty in the recruitment deviates. This allows the impact of misspecification of density dependence to be evaluated, i.e. if $F_{MSY}$ is underestimated then yield will be less than MSY, while if $F_{MSY}$ is overestimated yield will be lost due to overfishing. Stochastic projections of the four Operating Models for the four estimates of $F_{MSY}$ are shown in **Figures X3a, X3b, X3c and X3d**

**Figure X4** summarizes the yields and SSBs obtained for each Operating Model under the correct and misspecified form of density dependence and the associated reference points.

@@

REMOVE

[ Ignoring density dependent processes when they would be happening is expected to lead to ... ]

[ The impact of assuming the wrong type of density-dependence processes, i.e. applying the reference points from the one density dependent operating model to a simulation with other density dependent processes, could lead to .... ]

>>>>

Each of the OMs were then projected for the values of $F_{MSY}$ based on the four assumptions about density dependence. This allows a comparison between the yield that could potentially be achieved and that forgone by making an incorrect assumption about density dependence. The OMs were first projected, without process error in recruitment, from the end of the historical estimates for a range of fishing mortality (spanning 0 to $F_{crash}$) for 30 years into the future. The estimates in the final year of the projections were then be used to construct equilibrium curves (**Figure 15**). The points on the curve correspond to the projected outcomes for the values of $F_{MSY}$ from each OM. This was run as a check, as the equilibrium and projections should agree, I.e. the points at MSY should be the same colour as the curve.

The OMs were also projected for the estimates of different estimates $F_{MSY}$, with stochasticty in the recruitment deviates. This allows the impact of misspecification of density dependence to be evaluated, i.e. if $F_{MSY}$ is underestimated then yield will be less than MSY, while if $F_{MSY}$ is overestimated yield will be lost due to overfishing. Stochastic projections of the four Operating Models for the four estimates of $F_{MSY}$ are shown in **Figures 16-19**. **Figure 20** summarizes the yields and SSBs obtained for each Operating Model under the correct and mis-specified form of density dependence.

@@

@@

$W_a = {\overline{W_a}} (B/B_{MSY})^{{\beta}_a}$

@@

$W_a = {\overline{W_a}} {(B/B_{MSY})^{{\beta}_a}$

@@

@@

*`r fig_nums("mse_sim2")`*

fig_nums(
  name    = "eq_check", level = 1, display = FALSE,
  caption = "Check of equilibrium curves against end points of simulated time series at $F_{MSY}$'s from all scenarios")

  knitr::include_graphics(path=
                            file.path(figuresdir,paste(section,mystk,"equilibrium_check.jpg",sep="_")))

*`r fig_nums("eq_check")`*

@@

The OMs were first projected, without process error in recruitment, from the end of the historical estimates for a range of fishing mortality (spanning 0 to $F_{crash}$) for 30 years into the future. The estimates in the final year of the projections were then be used to construct equilibrium curves (**Figure 15**). The points on the curve correspond to the projected outcomes for the values of $F_{MSY}$ from each OM. This was run as a check, as the equilibrium and projections should agree, I.e. the points at MSY should be the same colour as the curve.

The OMs were also projected for the estimates of different estimates $F_{MSY}$, with stochasticty in the recruitment deviates. This allows the impact of misspecification of density dependence to be evaluated, i.e. if $F_{MSY}$ is underestimated then yield will be less than MSY, while if $F_{MSY}$ is overestimated yield will be lost due to overfishing. Stochastic projections of the four Operating Models for the four estimates of $F_{MSY}$ are shown in **Figures 16-19**

**Figure 20** summarizes the yields and SSBs obtained for each Operating Model under the correct and misspecified form of density dependence and the associated reference points.

@@
